Learning \strips\ action models with classical planning

### 2018-01-31 doc/icaps-18/camera-ready/strips-learning.tex
Acknowledgements, short background, bibliography

A {\em classical planning frame} is a tuple $\Phi=\tup{F,A}$, where $F$ is a set of fluents and $A$ is a set of actions. Each action $a\in A$ comprises three sets of literals:
\begin{itemize}
\item $\pre(a)\subseteq\mathcal{L}(F)$, called {\em preconditions}, the literals that must hold for the action $a\in A$ to be applicable.
\item $\eff^+(a)\subseteq\mathcal{L}(F)$, called {\em positive effects}, that defines the fluents set to true by the application of the action $a\in A$.
\item $\eff^-(a)\subseteq\mathcal{L}(F)$, called {\em negative effects}, that defines the fluents set to false by the action application.
\end{itemize}
We say that an action $a\in A$ is {\em applicable} in a state $s$ iff $\pre(a)\subseteq s$. The result of applying $a$ in $s$ is the {\em successor state} $\theta(s,a)=\{s\setminus\eff^-(a))\cup\eff^+(a)\}$.

@@

% Commented for blind submission
\begin{small}
\subsection*{Acknowledgment}
Diego Aineto is partially supported by the {\it FPU} program funded by the Spanish government. Sergio Jim\'enez is partially supported by the {\it Ramon y Cajal} program funded by the Spanish government.
\end{small}

\bibliographystyle{aaai}
\bibliography{strips-learning}
\end{document}

>>>>

A {\em classical planning frame} is a tuple $\Phi=\tup{F,A}$, where $F$ is a set of fluents and $A$ is a set of actions. An action $a\in A$ is defined with {\em preconditions}, $\pre(a)\subseteq\mathcal{L}(F)$, {\em positive effects}, $\eff^+(a)\subseteq\mathcal{L}(F)$, and {\em negative effects} $\eff^-(a)\subseteq\mathcal{L}(F)$. We say that an action $a\in A$ is {\em applicable} in a state $s$ iff $\pre(a)\subseteq s$. The result of applying $a$ in $s$ is the {\em successor state} denoted by $\theta(s,a)=\{s\setminus\eff^-(a))\cup\eff^+(a)\}$.

We say that an action $a\in A$ is {\em applicable} in a state $s$ iff $\pre(a)\subseteq s$. The result of applying $a$ in $s$ is the {\em successor state} $\theta(s,a)=\{s\setminus\eff^-(a))\cup\eff^+(a)\}$.

@@

% Commented for blind submission
\begin{small}
\subsection*{Acknowledgment}
This work is supported by the Spanish MINECO project TIN2017-88476-C2-1-R. Diego Aineto is partially supported by the {\it FPU16/03184} and Sergio Jim\'enez by the {\it Ramon y Cajal}, both programs funded by the Spanish government.
\end{small}

\bibliographystyle{aaai}
\bibliography{planlearnbibliography}
\end{document}
